\documentclass[a4paper,11pt]{article}

\usepackage[margin=2.5cm]{geometry}
\usepackage{parskip}
\usepackage{setspace}
\usepackage[hidelinks]{hyperref}

\begin{document}

\onehalfspacing

\noindent

\begin{flushright}
Oliver Ekeberg \\
Oslo, Norway \\
+47 941 35 068 \\
\href{mailto:oliveroekeberg@gmail.com}{oliveroekeberg@gmail.com} \\
\vspace{0.5cm}
\today
\end{flushright}

\vspace{1cm}

\noindent
Hiring Team \\
Statkraft AS \\
Düsseldorf, Germany

\vspace{1cm}

Dear Hiring Team,

I am applying for the Portfolio Strategy Intern position in Southern European Origination starting 2 March 2026. I am currently studying Applied Mathematics and Computational Science at the University of Oslo, and I hold a BSc in Data Science for Business from BI Norwegian Business School. This combination allows me to work comfortably with quantitative models while also understanding the commercial context they are applied to.

I am particularly interested in portfolio management and trading within power and renewable energy markets, where pricing, risk, and exposure directly affect business outcomes. I find Statkrafts culture and environment appealing, and I am motivated by Statkraft’s “one team – one PnL” approach, which closely links analytics to real transactions.

Previously, as a Risk Analyst in a student-managed investment fund, I worked with portfolio data, automation, and stress testing in Python, supporting risk and scenario analysis for investment decisions. Alongside this, my academic work has involved building mathematical simulations and optimization-based models, with a strong focus on control theory, understandability and scalability. 

I am motivated, structured, and eager to further develop my understanding of power markets, renewables, and portfolio strategy in an applied setting. I would welcome the opportunity to discuss my application further.

\vspace{1cm}

\noindent
Kind regards,\\
Oliver Ekeberg

\end{document}
