%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,10pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    }
    {
    \end{minipage}
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}
    }




%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{}C@{}}
\Huge{Oliver Ekeberg} \\[7.5pt]
\href{https://github.com/OliverOE1509}{\raisebox{-0.05\height}\faGithub\ OliverOE1509} \ $|$ \ 
\href{https://linkedin.com/in/oliver-ekeberg}{\raisebox{-0.05\height}\faLinkedin\ oliver-ekeberg} \ $|$ \ 
\href{https://mysite.com}{\raisebox{-0.05\height}\faGlobe \ mysite.com} \ $|$ \ 
\href{mailto:email@mysite.com}{\raisebox{-0.05\height}\faEnvelope \ email@mysite.com} \ $|$ \ 
\href{tel:+000000000000}{\raisebox{-0.05\height}\faMobile \ +47.941.35.068} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}

Mathematics and data science student passionate about artificial intelligence, machine learning, and high-performance computing. Skilled in Python, SQL, and statistical modeling, with hands-on experience in Docker, Kubernetes, CUDA, and GPU-accelerated training. Strong interest in applying advanced AI and computational methods to quantitative finance and large-scale data systems.
%Experience
\section{Work Experience}

\begin{joblong}{Risk Analyst, BISO Invest}{Sep 2023 -- Aug 2024}
    \item Developed an API (Python, Wireshark) to extract and format portfolio holdings for automated stress testing.  
    \item Built quantitative models for risk analysis, including volatility forecasting and parameter fitting.  
\end{joblong}

\begin{joblong}{Participant, KPMG x ServiceNow Hackathon}{Feb 2024}
    \item Collaborated in a team of students and KPMG consultants to design and deliver a functional client solution in ServiceNow.  
    \item Gained hands-on experience with ServiceNow workflows and rapid prototyping under time pressure.  
    \item Presented solution to a jury of KPMG partners, ServiceNow experts, and clients.  
\end{joblong}

\begin{joblong}{Part-time Worker, REMA 1000}{Oct 2024 -- present}
    \item Delivered customer service in a high-volume retail environment, further strengthening communication skills.  
    \item Supported daily operations through teamwork and adaptability, while enhancing problem solving skills
\end{joblong}


  
%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{@{}l X r@{}}
\textbf{Robotic Arm with Lamp} & \hfill \href{https://github.com/OliverOE1509/robotic-arm}{GitHub} & 2025 \\[3.75pt]
\multicolumn{3}{@{}p{\linewidth}@{}}{Designed and 3D-printed a 5-DOF robotic arm in FreeCAD, powered by Raspberry Pi + servo motors. Integrated a control system for positioning and attached a lamp as the end effector. Project developed to gain hands-on experience with electronics and hardware integration.} \\[1ex]

\textbf{Reinforcement Learning Game} & \hfill \href{https://github.com/OliverOE1509/}{GitHub} & 2025 \\[3.75pt]
\multicolumn{3}{@{}p{\linewidth}@{}}{Created a custom 2D two-player game environment. Implemented reinforcement learning agents to explore cooperative and competitive strategies using Gymnasium-compatible APIs. Collaborated with Daniel Gr{\o}nhaug to extend the framework towards real-world 3D drone control as part of the AI Fight Club competition hosted by Lockheed Martin.} \\

\textbf{Game Theory Research (Quantitative Economics)} & 2023 \\[3.75pt]
\multicolumn{3}{@{}p{\linewidth}@{}}{Co-authored a 20+ page research paper applying game theory to the Prisoner’s Dilemma. Explored the impact of alternative strategies on cooperative and competitive outcomes, and analyzed their influence on equilibrium dynamics. Our research used 4 different strategies, and analyze how the winning strategy of each game depended on discount rate} \\[1ex]


\end{tabularx}


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}

2021 -- 2024 & 
BSc, Data Science for Business, \textbf{BI Norwegian Business School} 
\hfill (GPA: 4.0/5.0) \\
& \textit{Selected courses:} 
\href{https://programmeinfo.bi.no/en/course/EBA-3530/2023-spring}{Machine Learning}, 
\href{https://programmeinfo.bi.no/nb/course/EBA-3650/2024-spring}{Quantitative Economics}, 
\href{https://programmeinfo.bi.no/nb/course/EBA-3420/2022-spring}{Programming in Python \& SQL} \\[1ex]

2024 -- present & 
BSc, Applied Mathematics and Computational Science, \textbf{University of Oslo} 
\hfill (GPA: 4.0/5.0) \\
& \textit{Selected courses:} 
\href{https://www.uio.no/studier/emner/matnat/math/MAT3110/h25/index.html}{Numerical Analysis}, 
\href{https://www.uio.no/studier/emner/matnat/math/MAT1125/h25/index.html}{Advanced Linear Algebra}, 
\href{https://www.uio.no/studier/emner/matnat/its/TEK4090/h25/index.html}{Control Theory \& Systems} \\

\end{tabularx}



%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Publications}
\begin{refsection}[citations.bib]
\nocite{*}
\printbibliography[heading=none]
\end{refsection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Programming & Python (NumPy, Pandas, Matplotlib, Scikit-learn, PyTorch), SQL, C++ \\
AI \& Data Science & Deep Learning, Reinforcement Learning, NLP \\
Mathematics \& Modeling & Linear Algebra, Numerical Analysis, Probability, Time Series, Optimization \\
Computing \& Tools & Docker, Kubernetes, Git/Github, Linux, LaTeX, CUDA, GPU-accelerated training \\
Finance \& Applications & Risk Management, Portfolio Analysis, Volatility Forecasting, Stress Testing \\
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
