%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,10pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.4\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.5pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    }
    {
    \end{minipage}
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.5pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=0.7em, itemsep=1pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}
    }




%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{}C@{}}
\Huge{Oliver Ekeberg} \\[7.5pt]
\href{https://github.com/OliverOE1509}{\raisebox{-0.05\height}\faGithub\ OliverOE1509} \ $|$ \ 
\href{https://linkedin.com/in/oliver-ekeberg}{\raisebox{-0.05\height}\faLinkedin\ oliver-ekeberg} \ $|$ \ 
\href{mailto:email@mysite.com}{\raisebox{-0.05\height}\faEnvelope \ oliveroekeberg@gmail.com} \ $|$ \ 
\href{tel:+000000000000}{\raisebox{-0.05\height}\faMobile \ +47 941 35 068} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}

Quantitative student in Applied Mathematics and Data Science with strong interest in energy markets, portfolio management, and trading. Experienced in Python-based data analysis, risk modeling, and automation of portfolio analytics. Motivated to apply quantitative methods to power markets, renewables, and commodity portfolios.
%Experience
\section{Work Experience}


\begin{joblong}{Risk Analyst, BISO Invest}{Sep 2023 -- Aug 2024}
    \item Built Python-based tooling to extract, clean, and structure portfolio holdings for automated risk and exposure analysis.
    \item Performed portfolio stress testing and scenario analysis under market shocks, volatility shifts, and correlation changes.
    \item Supported portfolio construction and monitoring through quantitative analysis of risk, return, and diversification effects.
    \item Worked closely with portfolio managers in a student-managed investment fund environment.
\end{joblong}


\begin{joblong}{Participant, KPMG x ServiceNow Hackathon}{Feb 2024}
    \item Solved a complex business problem under tight deadlines using structured analysis and rapid prototyping.
    \item Translated qualitative problem statements into quantitative workflows and decision-support tools.
    \item Presented solution to senior consultants, partners, and clients.
\end{joblong}


\begin{jobshort}{Part-time Worker, REMA 1000}{Oct 2024 -- present}
Customer-facing role in a high-pressure retail environment, strengthening communication, reliability, and execution.
\end{jobshort}


  
%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{@{}l X r@{}}
\textbf{Robotic Arm with Lamp} & \hfill \href{https://github.com/OliverOE1509/robotic-arm}{GitHub} & 2025 \\[3.75pt]
\multicolumn{3}{@{}p{\linewidth}@{}}{Designed and 3D-printed a 5-DOF robotic arm in FreeCAD, powered by Raspberry Pi + servo motors. Integrated a control system for positioning and attached a lamp as the end effector. Project developed to gain hands-on experience with electronics and hardware integration.} \\[1ex]

\textbf{Reinforcement Learning Environment} & 2025 \\[3.75pt]
\multicolumn{3}{@{}p{\linewidth}@{}}{
Designed a reinforcement learning environment with state, action, and reward structures under uncertainty. Focus on long-term reward optimization, risk-reward tradeoffs, and policy learning. Relevant to algorithmic trading, energy dispatch decisions, and storage optimization.
} \\[1ex]


\textbf{Multi-Agent Control \& Optimization (Drone Swarm)} & 2023 \\[3.75pt]
\multicolumn{3}{@{}p{\linewidth}@{}}{
Developed decentralized decision-making and optimization algorithms in a multi-agent system under uncertainty. Implemented cost-based bidding mechanisms, Model Predictive Control (MPC), and risk-aware path planning. Strong parallels to portfolio optimization, exposure management, and decision-making under stochastic dynamics.
} \\[1ex]



\end{tabularx}


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}

2021 -- 2024 & 
BSc, Data Science for Business, \textbf{BI Norwegian Business School} 
\hfill (GPA: 4.0/5.0) \\
& \textit{Selected courses:} 
\href{https://programmeinfo.bi.no/en/course/EBA-3530/2023-spring}{Machine Learning}, 
\href{https://programmeinfo.bi.no/nb/course/EBA-3650/2024-spring}{Quantitative Economics}, 
\href{https://programmeinfo.bi.no/nb/course/EBA-3420/2022-spring}{Programming in Python \& SQL} \\
& Focus on quantitative modeling, optimization, and data-driven decision making in economic and financial systems.
\\[1ex]

2024 -- present & 
BSc, Applied Mathematics and Computational Science, \textbf{University of Oslo} 
\hfill (GPA: 4.0/5.0) \\
& \textit{Selected courses:} 
\href{https://www.uio.no/studier/emner/matnat/math/MAT3110/h25/index.html}{Numerical Analysis}, 
\href{https://www.uio.no/studier/emner/matnat/math/MAT1125/h25/index.html}{Advanced Linear Algebra}, 
\href{https://www.uio.no/studier/emner/matnat/its/TEK4090/h25/index.html}{Control Theory \& Systems} \\

& Emphasis on numerical methods, stochastic systems, and optimization relevant to pricing and portfolio models.

\end{tabularx}



%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
%\section{Publications}
%\begin{refsection}[citations.bib]
%\nocite{*}
%\printbibliography[heading=none]
%\end{refsection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Quantitative Analysis & Portfolio Risk, Scenario Analysis, Optimization, Stochastic Modeling \\
Programming & Python (NumPy, Pandas, Matplotlib, SciPy), SQL, MATLAB \\
Markets \& Finance & Portfolio Management, Volatility Modeling, Stress Testing, Asset Pricing \\
Energy \& Commodities & Power Markets (fundamentals), Renewables, Storage Economics (BESS) \\
Tools & Excel (advanced), Docker, Git, Linux, LaTeX \\
\end{tabularx}

\end{document}
