\documentclass[a4paper,11pt]{article}

\usepackage[margin=2.4cm]{geometry}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}

\begin{document}
\onehalfspacing

% ===== Header =====
\begin{flushright}
\textbf{Oliver Ekeberg} \\
Oslo, Norway \\
+47 941 35 068 \\
\href{mailto:oliveroekeberg@gmail.com}{oliveroekeberg@gmail.com} \\
\href{https://linkedin.com/in/oliver-ekeberg}{LinkedIn} \ $|$ \
\href{https://github.com/OliverOE1509}{GitHub} \\
\vspace{0.4cm}
January 2026
\end{flushright}

\vspace{0.8cm}

\noindent
Hiring Team \\
Redstone Group \\
London

\vspace{0.8cm}

% ===== Body =====
\noindent
Dear Hiring Team,

I am applying for the Trading Analyst / Junior Trader position in Commodities Trading at Redstone Group. Quantitative student combining business and applied mathematics; focused on commodity markets, risk, and trading automation.

I am motivated by commodity markets because they combine fundamentals, risk, and fast decision-making under uncertainty. Your focus on commodity markets and trading decision-making, where strong analysis and fast iteration translate directly to commercial outcomes. A role combining market analysis, risk thinking, and automation—building tools and insights traders actually use.

Built Python tooling to extract, clean, and structure portfolio holdings for automated exposure monitoring and stress testing. Worked comfortably with time series data (feature engineering, aggregation, validation) for analysis and forecasting tasks. Performed scenario analysis under market shocks and volatility/correlation changes; communicated key drivers and risk concentration.

I would welcome the opportunity to discuss how I can contribute to your trading team.

\vspace{0.9cm}

\noindent
Kind regards,\\
Oliver Ekeberg

\end{document}
